RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2015-01-13 manuscripts/manuscript.Rmd
update vignettes

```{r echo=FALSE}
install.packages("RNeXML", dependencies=TRUE)
library(RNeXML)
```

@@

```{r cleanup, include=FALSE, cache=FALSE}
unlink("simmap.xml")
unlink("birds.xml")
unlink("geospiza.xml")
unlink("rdf_meta.xml")
```

>>>>

```{r echo=FALSE, results='hide'}
install.packages("RNeXML", dependencies=TRUE)
library(RNeXML)
```

@@

```{r cleanup, include=FALSE, cache=FALSE}
unlink("birds.xml")
unlink("geospiza.xml")
```
